A Structural and Functional Bioinformatics Study of QTY-designed Opsins

### 2025-04-22 Paper/Source/manuscript.tex
Switch to Overleaf TeX. Add RGR and RRH to all OPN superimposition

\documentclass[fleqn,10pt,lineno]{manuscript}
%%\usepackage{setspace}
%%\doublespacing
\usepackage{soul}
\usepackage[utf8]{inputenc}

@@

\title{A Structural and Functional Bioinformatics Study of QTY-designed Retinylidene Proteins}

@@

Abstract of paper -- leave until everything is written.

@@

\textbf{* Families of opsins - vertebrate vs. bacterial}

@@

\textbf{* General features of vertebrate opsin; structure and function; activation mechanism of rhodopsin; may include existing rhodopsin bioinformatics studies?}

GPCR, 7TM. 
RHO: rhodopsin is exemplary; earliest GPCR studied, bovine rhodopsin. 
Lysine-retinal schiff base linkage, conserved evolutionarily. 
Delocalized electrons in retinal, receive photon, high activation rate. 
11-cis to all-trans isomerization.
RHO: dark >> batho >> lumi >> meta I <<>> meta II; proton-transfer pathway. 
TM6 outward. 
Activates G-protein, initiate secondary messenger cascade.

\textbf{* Expression, function of each vertebrate opsin}

The OPN family preferentially binds 11-cis-retinal and catalyzes its isomerization to all-trans-retinal via a retinochrome mechanism.

@@

OPN2 (Opsin 2), also known as rhodopsin, is expressed in retinal rod photoreceptors and essential for light transduction and vision at low light intensity. It is correlated with retinitis pigmentosa 4, characterized by retinal pigments deposits, loss of night vision, loss of peripheral visual field, and eventual loss of central visual field. Autosomal dominant night blindness, a non-progressive impairment of night vision, is also attributed to mutation of OPN2.

@@

RRH (visual pigment-like receptor), also known as peropsin, is localized in the microvilli of RPE that surround photoreceptor outer segments. It may play a role in RPE physiology either by detecting light directly or by monitoring the concentration of retinal. FUNCTION?

\textbf{* General features of bacterial opsin; structure, function, applications}

@@

\textbf{* Expression, function of each bacterial opsin}

BACR, or bacteriorhodopsin, is a 7TM protein that forms a trimer light-driven proton pump. It binds to 13-cis-retinal and catalyzes the isomerization to all-trans-retinal? Studied... Applications...

BACH, or halorhodopsin, is a 7TM protein that forms a trimer light-driven chloride pump. It binds to 13-cis-retinal and catalyzes the isomerization to all-trans-retinal? Studied... It is activated by yellow light and is used as a tool of inhibition in optogenetics. More applications...

ChR2, or channelrhodopsin 2, is a 7TM protein that forms a dimer light-activated sodium channel. It binds to 13-cis-retinal and catalyzes the isomerization to all-trans-retinal? Studied... It is activated by blue light and is used as a tool of excitation in optogenetics. More applications...

@@

@@

@@

* describe, explain, discuss MD results (Fig3 and Fig4)
	- I need more discussion here

@@

\section*{Acknowledgments}

@@

\begin{table}[h]
	\centering
	\caption{Protein characteristics}
	\label{tb:characteristics}
	\includegraphics[width=\linewidth]{Figures/characteristics.jpg}
\end{table}

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{Figures/sequences.jpg}
	\caption{Protein sequence alignments}
	\label{fig:sequences}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{Figures/superimposition-human.jpg}
	\caption{Superimposition of human retinylidene proteins}
	\label{fig:humansup}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{Figures/superimposition-bacterial.jpg}
	\caption{Superimposition of bacterial retinylidene proteins}
	\label{fig:bacterialsup}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{Figures/pairwise.jpg}
	\caption{Pairwise comparison of human opsins}
	\label{fig:pairwise}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{Figures/hydrophobicity.jpg}
	\caption{Surface hydrophobicity}
	\label{fig:hydrophobicity}
\end{figure}

>>>>

\documentclass[fleqn,10pt,lineno]{manuscript}
%%\usepackage{setspace}
%%\doublespacing
\usepackage{soul, hyperref}
\usepackage[utf8]{inputenc}

@@

\title{A Structural and Functional Bioinformatics Study of QTY-designed Opsins}

@@

This study investigates the QTY design of 9 human opsins and 3 microbial opsins, all of which bind retinal as the ligand.

@@

\textbf{* Families of opsins - animal vs. microbial}

\citep{Spudich_2000}

@@

\textbf{* General features of animal opsin; structure and function; activation mechanism of rhodopsin; may include existing rhodopsin bioinformatics studies?}

Class A GPCR, 7TM, NPxxY motif, outward movement of TM6. \citep{Sakmar_2002, Zhou_2019}
296 Lys in TM7 \citep{Guhmann_2022}.
Lysine-retinal schiff base linkage, conserved evolutionarily. 
Delocalized electrons in retinal, receive photon, high activation rate. 
11-cis to all-trans isomerization.
RHO: dark >> batho >> lumi >> meta I <<>> meta II; proton-transfer pathway. 
TM6 outward. 
Activates G-protein, initiate secondary messenger cascade.

\textbf{* Expression, function of each animal opsin}

The OPN family preferentially binds 11-cis-retinal and catalyzes its isomerization to all-trans-retinal via a retinochrome mechanism. 
Evolutionarily distinct animal opsins \citep{Terakita_2005, Shichida_2009}

@@

OPN2 (Opsin 2), also known as rhodopsin, is expressed in retinal rod photoreceptors and essential for light transduction and vision at low light intensity. It is correlated with retinitis pigmentosa 4, characterized by retinal pigments deposits, loss of night vision, loss of peripheral visual field, and eventual loss of central visual field. Congenital stationary night blindness, a non-progressive autosomal dominant impairment of night vision, is also attributed to mutation of OPN2. 
RHO: rhodopsin is exemplary; earliest opsin studied, earliest crystal structure of GPCR \citep{Palczeski_2000} bovine rhodopsin.

@@

RRH (RPE-derived Rhodopsin Homolog), also known as peropsin, is localized in the microvilli of RPE that surround photoreceptor outer segments. It may play a role in RPE physiology either by detecting light directly or by monitoring the concentration of retinal. FUNCTION?

\textbf{* General features of microbial opsin; structure, function, applications}

@@

\textbf{* Expression, function of each microbial opsin}

\citep{Findlay_1986, Zhang_2011}
BACR, or bacteriorhodopsin, is a 7TM protein that forms a trimer light-driven proton pump.Studied... Applications...
BACH, or halorhodopsin, is a 7TM protein that forms a trimer light-driven chloride pump. Studied... It is activated by yellow light and is used as a tool of inhibition in optogenetics. More applications...
ChR2, or channelrhodopsin 2, is a 7TM protein that forms a dimer light-activated sodium channel. Studied... It is activated by blue light and is used as a tool of excitation in optogenetics. More applications...
All-trans to 13-cis? 
BACH \citep{Baselt_1989, Kouyama_2018}. BACR \citep{Taguchi_2023}. ChR2 \citep{Nagel_2005, Ardevol_2018, Xin_2023}.

"Recently, researchers built on top of ProteinMPNN to devise SolubleMPNN trained on only soluble proteins, which was applied to engineer soluble variants of bacteriorhodopsin, successfully converting a membrane protein into a soluble one, while maintaining its core function and ligand-binding ability (Nikolaev et al., 2024)."

@@

"Instead of taking a computational approach, we applied the QTY code to systematically engineer watersoluble analogs with reduced hydrophobicity in membrane proteins. The QTY concept was inspired by high-resolution (1.5\AA) electron density maps, which revealed structural similarities between hydrophobic and polar amino acids leucine (L) vs glutamine (Q); isoleucine (I)/valine (V) vs threonine (T); and phenylalanine (F) vs tyrosine (Y) (Zhang et al., 2018; Zhang \& Egli 2022; Tegler et al., 2020). In our previous experiments, using the simple and straightforward QTY code, we successfully bioengineered detergent-free chemokine (Zhang et al., 2018; Qing et al., 2019; Tegler et al., 2020), cytokine receptors (Hao et al., 2020) and bacterial histidine kinase (Li et al 2024). After these detergent-free membrane proteins were expressed and purified, these QTY analogs demonstrated structural stability, retained their ligand-binding capabilities and intact four enzymatic activities, making them ideal candidates for further studies and use them as antigens to generate therapeutic monoclonal antibodies."

"In May 2024, AlphaFold was upgraded to version 3 as AlphaFold 3, featuring an enhanced diffusion-based architecture that enables accurate prediction of multiple structures of protein complexes. Additionally, AlphaFold 3 extends its capabilities beyond protein structure prediction to include DNA, RNA, and small molecules including ligands and other proteins (Abramson et al., 2024)"

@@

SUMMARY.

@@

* describe, explain, discuss MD results (Fig3 and Fig4)
        - no changes to the NPxxY motif or retinal-binding Lys
	- I need more discussion here

@@

\section*{Acknowledgements}

@@

\begin{table}[htbp]
	\centering
	\caption{Protein characteristics}
	\label{tb:characteristics}
	\includegraphics[width=\linewidth]{Figures/characteristics.jpg}
\end{table}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/sequences.jpg}
	\caption{Protein sequence alignments}
	\label{fig:sequences}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/superimposition-human.jpg}
	\caption{Superimposition of human retinylidene proteins}
	\label{fig:humansup}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/superimposition-microbial.jpg}
	\caption{Superimposition of microbial retinylidene proteins}
	\label{fig:microbialsup}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/pairwise.jpg}
	\caption{Pairwise comparison of human opsins}
	\label{fig:pairwise}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/hydrophobicity.jpg}
	\caption{Surface hydrophobicity}
	\label{fig:hydrophobicity}
\end{figure}
